Blum axioms and nondeterministic computation of functions

### 2015-12-16 paper.tex
paper.tex: Add Valiant's #P class.

\subsection{Valiant's $\#\P$ class}
\subsection{Alternative approaches for nondeterministic functions}

>>>>

\subsection{Valiant's $\#\P$ class}

As observed by Krentel,
the definition of $\OptP$ was achieved by applying
an associative and commutative operator to the set of values
that the nondeterministic machine returns.
Thus,
for every different operator we choose,
we have an alternative definition of nondeterministic computation of functions.
We mention only one such alternative definition,
due to Valiant \cite{Valiant1979}.

\begin{definition}
    If every branch of the computation of $M$ on $x$ halts,
    define the value returned by $M$ on $x$
    as being the number of different accepting branches of computation.
\end{definition}

In the same way that Krentel defined his $\OptP$ class using polynomial bounds,
Valiant's $\#\P$ class is the set of all functions
that can be computed in polynomial time by nondeterministic machines
according to the above definition.
